Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-05 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: style

\noindent Airborne hyperspectral data with a spatial resolution of one meter and 126 spectral bands was available for four Monterey Pine (\textit{Pinus radiata}) plantations in northern Spain.
The trees in the study area plots suffer from infections of invasive pathogens such as \textit{Diplodia sapinea}, \textit{Fusarium circinatum}, \textit{Armillaria mellea} or \textit{Heterobasidion annosum}, leading to a spread of cankers or defoliation~\cite{mesanza2016, iturritxa2017}.
In-situ measurements of defoliation at trees (serving as a proxy for tree health) were collected to serve as the response variable \textit{defoliation} which ranges from 0\% - 100\% (\autoref{fig:defol-distr}). % chktex 8
The fungi are assumed to infect the trees through open wounds, possibly caused by previous hail damage \cite{iturritxa2014}.
The dieback of these trees, which are mainly used as timber, causes high economic damages \cite{ganley2009}.

>>>>

\noindent Airborne hyperspectral data with a spatial resolution of one meter and 126 spectral bands was available for four Monterey Pine (\textit{Pinus radiata}) plantations in northern Spain.
The trees in the study area plots suffer from infections of invasive pathogens such as \textit{Diplodia sapinea}, \textit{Fusarium circinatum}, \textit{Armillaria mellea} or \textit{Heterobasidion annosum}, leading to a spread of cankers or defoliation~\cite{mesanza2016, iturritxa2017}.
In-situ measurements of defoliation at trees (serving as a proxy for tree health) were collected to serve as the response variable \textit{defoliation} which ranges from 0 - 100 (in \%) (\autoref{fig:defol-distr}).
The fungi are assumed to infect the trees through open wounds, possibly caused by previous hail damage \cite{iturritxa2014}.
The dieback of these trees, which are mainly used as timber, causes high economic damages \cite{ganley2009}.
